---
title: 'Homework 5: Multiple Contacts and Time-dependent Transition Probability'
author: "YOUR NAME HERE"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
```

## Instructions:

1. Please replace "YOUR NAME HERE" under author above with your name before you knit your final document for submission.
2. All of your homework needs to be completed in this document, whether it requires R or just typed responses. As we incorporate more statistical computing into the course, it will be important that you are comfortable with R Markdown, so start now. Remember that R Markdown gives us a convenient framework for reproducible statistical reports because it contains a complete record of our analyses and conclusions.
3. You may knit to PDF, HTML, or Word (click on the drop-down menu for Knit to choose the file output type). 
4. Before submitting your work, please make sure the knitted file is well organized, legible, and looks the way you expect!
5. Please include the names of any classmates with whom you worked on this homework, as well as any external resources that you might have used.
6. This homework assignment is **due on Friday, March 8, 2024 and should be submitted to Gradescope**.

- *Collaborators:*

- *External resources:*

## Computational and Conceptual Questions

**Question CCQ 1. Consider an infection where the effective number of contacts per day is 2 and the duration of infectiousness is 3 days. What is the basic reproductive number?**



**Question CCQ 2. Consider an infection where the basic reproductive number is 14 and the effective number of contacts is 2 per day. What is the duration of infectiousness (include appropriate time scale)?**



**Question CCQ 3. Consider an infection where the basic reproductive number is 10 and the duration of infectiousness is 10 days. What is the effective number of contacts per day?**


**Question CQ 4. Suppose $R_0$ is the identical in two populations, but one population is 500,000 and the other is 1 million. In which population will $\lambda_t$ be smaller for the same time point? Why?**


## HIV

For sexually-transmitted infections (primary mode of transmission for HIV), we need to make a slight modification to the $S\rightarrow I$ transition parameter. In this case, because sexual contacts are easy to track (relative to contacts associated with respiratory transmission, for example), we can decompose $c_e$ into two components, the number of sexual contacts per unit time ($k_s$), and the probability of infection given contact between a susceptible and infectious individual ($p^c(t)$). In this case, 

$$\lambda_t=1-\exp\left\{- k_sp^c(t)\times \frac{I_{t-1}}{N}\right\};$$

$k_sp^c(t)$ is replacing $c_e$ in this case. This allows us to investigate the effect of sexual activity level. As before, we will assume $p^c(t)$ is constant for now. 

**(a) Modify your code from Homework 4 Part (b) **to include this new representation of $\lambda_t$**. You can assume that $k_s=3$ sexual contacts per week; $p^c(t)$ is given in Homework 5 for Part (b).**

```{r}

```

**(b) Plot the results of your simulation (compartment versus time). For full credit, you should plot all the compartments in the same plot for full credit - the easiest way to do this is in ggplot2.**

```{r}

```


**(c) How does this compare to the results you found in Homework 4 Part (b)? Which do you think is a more realistic depiction of this infection process?**



